---
title: "CVS stratified"
author: "Lucas Hoogduin and Paul Touw"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CVS stratified}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

We want to estimate the total population value of a population of inventories. The sampling frame `inventoryData` is part of the `FSaudit` package. The data of our sampling procedure are stored in a `cvs_obj` CVS object.

```{r}
RNGkind(sample.kind = "Rounding")
library(FSaudit)
myStrat <- cvs_obj(bv = inventoryData$bv, id = inventoryData$item)
```
We first show how a population is stratified into three strata with equal recorded values boundaries.
```{r}
myStrat <- stratify(myStrat, stratMeth = "equal", strata = 3)
myStrat$stratSumm
```
We can also use the `cumulative square root of the sum of the squares` method.
```{r}

myStrat <- stratify(myStrat, stratMeth = "cumulative", strata = 3, classes = 10)
```
An overview of the details of the classes used is given by
```{r}
myStrat$classSumm
```
The resulting stratification is
```{r}
myStrat$stratSumm
myStrat$alloc
```
## Sample size calculation
We continue with the `cumulative` stratification method. We can use a preassigned sample size, for instance when the auditor first executes a *pilot sample* to get a feel of the standard deviation of the audit values. For example, if the auditor first wants to test 400 sampling units, we can preassign the sample size attribute $n$ in the `cvs_obj`.

```{r}
myStrat <- stratify(myStrat, stratMeth = "cumulative", strata = 3, classes = 10, n = 400)
myStrat$alloc
```
The preassigned sample size is allocated to the strata, using Neyman allocation.

On the other hand, the auditor can also request `FSaudit` to calculate the required sample size for a given desired precision.

```{r}
myStrat <- size(myStrat, desPrec = 200000)
myStrat$n
myStrat$alloc
```
The required sample size is 584. Due to rounding in the allocation process, the sum of the stratum sample sizes $n_h$  is slightly lower.
```{r}
sum(myStrat$alloc$nh)
```
### Selection of sampling units

```{r}
myStrat <- select(myStrat, seed = 12345)
head(myStrat$sample)
```


### Evaluation

We obtain the true values of the sampling units.

```{r}
audit_values <- inventoryData[match(myStrat$sample$item,
                                   inventoryData$item),
                             c("item", "av")]
```


And then evaluate the sample.
```{r}
myStrat <- evaluate(myStrat, av = audit_values$av)
```


General results

```{r}
myStrat$evalResults$Estimates

```
We see that for the MPU estimator, desired precision of 200,000 is not achieved. It is for the other estimators.

Details of the individual estimators are also stored in the `cvs_obj`, for example for the MPU estimator:
```{r}
myStrat$evalResults$`Mean per unit estimation`
```
Or for the regression estimator:
```{r}
myStrat$evalResults$`Regression estimation`
```

