---
title: "Estimating the population mean and fraction"
author: "Lucas Hoogduin and Paul Touw"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Estimating the population mean and fraction}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette we will use one single data file, so you can get familiar with estimating a mean, a fraction, and their respective confidence intervals without learning the specifics of many different data sets. The `salaries` dataset contains salary details of 2,222 employees of the imaginary town of Winesbury, and is included with the `FSaudit` package. The data file indicates for each employee the Grade, Step within the Grade, and Gross salary, as well as a unique employee ID. The field Gender is coded with a 1 for female and a 0 for male.

Details of the data file can be obtained using base `R` functionality.

```{r}
library(FSaudit)
names(salaries)
(N <- nrow(salaries))
```

With sampling, we will try to estimate the population mean of gross salaries, and the population fractions of females and males. For the entire population, the recorded values are:

```{r}
sum(salaries$gross)
sum(salaries$sex) / N
```

## Draw a sample

Warning: as of version 3.6 of R, fundamental changes have been made in the random number generator. The default setting of the random number generator should
normally not be changed, but for the benefit of readers who use an older
version of R we set it to Rounding, which was the default prior to version 3.6.

We start with drawing *pilot sample* of `n = 50` sampling units. We also set the `seed` to a predetermined number, so that the results can be reperformed. The `head` function helps us to see the first few lines of the sample dataframe.

```{r}
RNGkind(sample.kind = "Rounding")
n <- 50
set.seed(12345)
sample1 <- salaries[sample(N, n), ]
head(sample1)
```
## Point estimate of the mean
Estimate mean gross amount.
```{r}
sum(sample1$gross)
(y_bar <- mean(sample1$gross))
```
Estimate total monthly gross payroll.
```{r}
N * y_bar
```
## Confidence intervals around the mean

### Two-sided intervals
First, we estimate the standard deviation of the gross amount in the population by calculating the sample standard deviation.
```{r}
(s <- sd(sample1$gross))
```
Standard error
```{r}
(se <- s / sqrt(n))
```
The relevant t-value for a 95\%, two-sided interval is obtained by use of the one-sided $t$-values at 2.5\% and 97.5\%. In general, if we desire a $1 - \alpha$ confidence interval, the relevant $t$-values are $\alpha / 2$ and $1 - \alpha /2$
```{r}
(tval_lb <- qt(0.025, df = (n - 1)))
(tval_ub <- qt(0.975, df = (n - 1)))
```

The lower and upper bounds on $\bar{y}$ are then
```{r}
(lowerBound <- y_bar + tval_lb * se)
(upperBound <- y_bar + tval_ub * se)
```
Note that since the $t$-distribution is symmetrical around 0, the two $t$-values only differ in sign. We could therefore use only a single one, and just change the sign in the calculation of one of the bounds.
```{r}
(tval <- qt(0.975, df = (n - 1)))
(lowerBound <- y_bar - tval * se)
(upperBound <- y_bar + tval * se)
```
Extrapolating this to the entire population we then get 
```{r}
y_hat <- N * y_bar
N * lowerBound
N * upperBound
```

Precision achieved
```{r}
(precAch <- N * tval * se)
```
### One-sided intervals
For one-sided intervals, for example to calculate the maximum gross amount at 95\% confidence, we do not split $\alpha$ into two tails, but apply it on one single tail.

```{r}
(tval2 <- qt(0.95, df = (n - 1)))
y_bar + tval2 * se
N * (y_bar + tval2 * se)
```
## Minimum sample size to estimate the mean

### Infinite populations
Required sample size for $E$ = 600,000
```{r}
E <- 600000
N^2 * tval^2 * s^2 / E^2
```
Draw additional sampling units. You can verify that by using the same random number seed, the first 50 sampling units in `sample2` are exactly the same as in the original sample.
```{r}
set.seed(12345)
sample2 <- salaries[sample(N, 131), ]
head(sample2)
```
We calculate the mean of the total sample.
```{r}
mean(sample2$gross)
```
Ignoring Stein's rule (See **Audit Data Analysis**).
```{r}
mean(sample2$gross)
(n2 <- nrow(sample2))
qt(0.975, n2 - 1)
sd(sample2$gross)
N * qt(0.975, df = n2 - 1) * sd(sample2$gross) / sqrt(n2)
N * mean(sample2$gross)
```
### Finite populations
Solve gamma

```{r}
E2 <- 300000
(gamma  <- E2^2 * (N - 1) / (N^2 * tval^2 * sd(sample1$gross)^2))
(N / (1 + gamma))
```

## Confidence intervals around a fraction
In a sample of $n = 50$ we find $k = 31$ women.
To calculate a confidence interval for a fraction in a finite population, we  employ the hypergeometric distribution.

Confidence bounds around a fraction are calculated in `R` with the `upper` and `lower` functions, that are part of the `FSaudit` package. The distribution `dist` is by default hypergeometric, alternative options are the binomial or the Poisson distributions.

In all cases, the point estimate is
```{r}
k <- 31
k / n * N
```
```{r}
lower(k = 31, popn = 2222, n = 50, alpha = .025)
upper(k = 31, popn = 2222, n = 50, alpha = .025)
```

Binomial approximation (answer provided as a fraction).
```{r}
lower(k = 31, n = 50, alpha = .025, dist = "binom")
upper(k = 31, n = 50, alpha = .025, dist = "binom")
```
Binomial approximation (answer provided as a number).
```{r}
lower(k = 31, popn = 2222, n = 50, alpha = .025, dist = "binom")
upper(k = 31, popn = 2222, n = 50, alpha = .025, dist = "binom")
```
Poisson approximation.
```{r}
lower(k = 31, popn = 2222, n = 50, alpha = .025, dist = "pois")
upper(k = 31, popn = 2222, n = 50, alpha = .025, dist = "pois")
```



