---
title: "MUS - Significant item selection"
author: "Lucas Hoogduin & Marcel Boersma"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MUS - Significant item selection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Introduction
In this vignette we show how to eliminate significant items. The function `significant` creates two lists, one list with significant items and another list with non-significant items. A subsequent function `select` selects a sample from the non-significant items, and stores the selection in the `sample` attribute in the MUS object. The auditor tests both the `significant` and `sample` lists. The `evaluate` function is only executed over the `sample` list and extends only to the population exclusive of the significant items.

### Ignoring significant items

We start with a MUS experiment
```{r}
library(FSaudit)
mySample <- mus_obj(cl = 0.95,
                    bv = accounts_receivable$amount,
                    id = accounts_receivable$invoice,
                    pm = 23950)
mySample <- size(mySample)
```
We can now show the sample size based on the entire population
```{r}
mySample$n
mySample$popBv
samplingInterval <- mySample$popBv / mySample$n
samplingInterval
```
With a sample size of `r mySample$n` and a total book value of the population `r prettyNum(sum(accounts_receivable$amount), big.mark = ",")`, all items greater than `r prettyNum(samplingInterval)` are deemed individually significant.

Let us first see what happens if we ignore these.
```{r}
mySample <- select(mySample,
                   selMeth = "fixed",
                   aggregates = TRUE,
                   seed = 1)
mySample$signItems
```
No elements are identified as being individually significant, because large items could be selected more than once.
```{r}
length(mySample$sample$bv)
mySample$n
```
A sample has been selected with a size of `r mySample$n`.

### Addressing significant items

We therefore need to run the `significant` function first before selecting the sample. This happens automatically when we set `aggregates = FALSE`.

```{r}
mySample2 <- mus_obj(cl = 0.95,
                     bv = accounts_receivable$amount,
                     id = accounts_receivable$invoice,
                     aggregates = FALSE,
                     pm = 23950)
mySample2 <- size(mySample2)
mySample2$n
mySample2$signItems
```
```{r}
mySample2 <- significant(mySample2)
mySample2$signItems
```
When eliminating the significant items, the sample size is recalculated.

```{r}
mySample2$n
```
We can then continue to select the sample.

```{r}
mySample2 <- select(mySample2,
                    selMeth = "fixed",
                    seed = 1)
length(mySample2$sample$bv)
```
We see that the appropriate number of elements have been selected from the population.
