---
title: "MUS - sample size"
author: "Lucas Hoogduin & Marcel Boersma"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MUS - sample size}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

MUS sample sizes are typically calculated using the (default) hypergeometric distribution. The `FSaudit` package also supports calculations with the approximating binomial and Poisson distributions.

We first load `FSaudit` as follows,

```{r, echo=TRUE}
library(FSaudit)
```
We then set up a sample from the Accounts Receivable population, that is included in the `FSaudit` package.
```{r}
mySample <- mus_obj(bv =  accounts_receivable$amount,
                    id = accounts_receivable$invoice,
                    pm = 450000,
                    ee = 100000,
                    evalMeth = "stringer")
```


### Hypergeometric

As the hypergeometric distribution is the default distribution, there is no need to specify it when calculating the sample size.

```{r}
mySample <- size(mySample)
mySample$n
```

### Binomial

The binomial distribution is a good approximation if the sample size is less than 10% of the population size.

The population size is given by the number of book values.

```{r}
populationSize <- length(accounts_receivable$amount)
populationSize
```
The sample size calculated with the hypergeometric distribution is `r mySample$n`, which is less than 10% of the population size of `r mySample$popn`. The calculation with the binomial should therefore be close.
```{r, echo = TRUE}
mySampleBinomial <- size(mySample, dist = "binom")
mySampleBinomial$n
```
### Poisson

The Poisson approximation used to be very useful in times when samples were planned manually. The approximation is reasonable for sample sizes $n \geq 20$ and population error rates $\pi < 0.10$.
The first condition is true, the second is false.
```{r}
populationErrorRate <- mySample$pm / mySample$popBv
populationErrorRate
```
Let us see if this has an effect on the sample size calculated.

```{r, echo = TRUE}
mySamplePoisson <- size(mySample, dist = "pois")
mySamplePoisson$n
```
We see that the Poisson approximation in this case is too conservative, leading to a sample size of `r mySamplePoisson$n` instead of the exact (hypergeometric) calculation of `r mySample$n`.
